%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cventries}
	
	%---------------------------------------------------------
	\cventry
	{Logistics Load Manager} % Job title
	{Walmart Supply Chain} % Organization
	{Grove City, Ohio} % Location
	{Jul. 2021 - Present} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Use a data driven approach to support innovation and intelligent risk-taking.}
			\item {Monitor and manage productivity of area of responsibility by 
				preparing, reviewing, and/or analyzing business reports.}
			\item {Dispatch drivers to move freight throughout the supply chain while
				maintaining safety, economic, and quality standards.}
			\item {Optimize routes with an astute consideration of outbound and inbound productivity.}
			\item {Communicate with stakeholders about service levels while prioritizing business needs.}
			\end{cvitems}
	}
	
	%---------------------------------------------------------
	\cventry
	{Systems Operator} % Job title
	{} % Organization
	{Mebane, North Carolina} % Location
	{Mar. 2021 - Jul. 2021} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Maintained operation of system hardware and software through monitoring functionality and performing preventative maintenance.}
			\item {Identified, reported, and resolved performance issues by following appropriate guidelines and procedures.}
			\item {Responded to critical systems issues and customer requests in a timely manner.}
			\item{Used data and facts to make decisions and involved others as needed.}
		\end{cvitems}
	}
	
	%---------------------------------------------------------
	\cventry
	{Stock Selector} % Job title
	{} % Organization
	{Henderson/Mebane, North Carolina} % Location
	{Sept. 2017 - Mar. 2021} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Fulfilled meat and produce orders to stores and clubs throughout North Carolina. }
			\item {Preserved a clean and orderly warehouse.}
			\item {Operated machinery with an emphasis on safety.}
			\item {Led peers towards improved safety, productivity, and quality standards.}
		\end{cvitems}
	}


	%---------------------------------------------------------
	\cventry
	{English Teacher} % Job title
	{Happy Marian English School} % Organization
	{Linkou Dist. New Taipei City, Taiwan (R.O.C.)} % Location
	{Oct. 2016 - Mar. 2017} % Date(s)
	{
		\begin{cvitems} % Description(s) of tasks/responsibilities
			\item {Taught ESL students with a primary focus on middle school level curriculum.}
			\item {Oversaw pre-school, 2nd, 4th, and 7th grade classrooms in a modernized private language school.}
			\item {Learned how to inspire, be inspired, and improve test scores.}
		\end{cvitems}
	}
	
	%---------------------------------------------------------

	
	%---------------------------------------------------------
\end{cventries}